### 2020-03-05 draft_ABP.tex
update

As shown in the last subsection, the $n$-dimensional permutahedron is associated 
with the set of all non-empty subsets of $[0,n]$, which is denoted by $\mathscr P_n$. 
Each facet of $P_n$ is lebeled by a non-empty proper subset $I$ of $[0,n]$, whose
equation is 
\begin{equation}
	F_J:=\sum_{J\neq \varnothing, J\subset I} S_J=0,
\end{equation}
so the number of facets of $\mathscr P_n$ is $2^n-2$. The AHBY condition 
can be solved from above equations:
\[
	S_I = (-1)^{|I|+1}\sum_{i\in I} S_i,
\]
for all non-empty subsets $I \subset [0,n]$ which are not singlets.

(proof of equations fo facets or ABHY condition?)

To get $u$-equations, we should solve $S_J$ by $F_J$ for eq.(\theequation), the 
solution is 
\[
	S_I=\sum_{J\neq \varnothing,J\subset I} (-1)^{|J|-|I|}F_J,
\]
then
\[
	\prod_{I\neq \varnothing,I\subset [0,n]}u_I^{F_I}=
	\prod_{I\neq \varnothing,I\subset [0,n]}x_I^{S_I}=
	\prod_{\varnothing\neq J\subset I\subset [0,n]}
	x_I^{(-1)^{|J|-|I|}F_J}=
	\prod_{J\neq \varnothing,J\subset [0,n]}
	\prod_{I\supset J}(x_I^{(-1)^{|J|-|I|}})^{F_J}
\]
gives that
\[
	u_I=\prod_{J\supset I}x_J^{(-1)^{|I|-|J|}}
\]

(notation!)

>>>>

As shown in the last subsection, the $n$-dimensional permutahedron is associated 
with the set of all non-empty subsets of $[0,n]$, which is denoted by $\mathscr P_n$. 
Each facet of $\mathscr P_n$ is lebeled by a non-empty proper subset $I$ of $[0,n]$, 
whose equation is 
\begin{equation}\label{Pnfacet}
	F_J:=\sum_{J\neq \varnothing, J\subset I} S_J=0,
\end{equation}
so the number of facets of $\mathscr P_n$ is $2^n-2$. The AHBY condition 
can be solved from above equations:
\[
	S_I = (-1)^{|I|+1}\sum_{i\in I} S_i,
\]
for all non-empty subsets $I \subset [0,n]$ which are not singlets.

(Zhenjie: proof of equations of facets or ABHY condition?)

To get $u$-equations, we should solve $S_J$ by $F_J$ from eq.\eqref{Pnfacet}, the 
solution is 
\begin{equation}\label{SinF}
	S_I=\sum_{J\neq \varnothing,J\subset I} (-1)^{|J|-|I|}F_J,
\end{equation}
then
\[
	\prod_{I\neq \varnothing,I\subset [0,n]}u_I^{F_I}=
	\prod_{I\neq \varnothing,I\subset [0,n]}x_I^{S_I}=
	\prod_{\varnothing\neq J\subset I\subset [0,n]}
	x_I^{(-1)^{|J|-|I|}F_J}=
	\prod_{J\neq \varnothing,J\subset [0,n]}
	\prod_{I\supset J}(x_I^{(-1)^{|J|-|I|}})^{F_J}
\]
gives that
\[
	u_I=\prod_{J\supset I}x_J^{(-1)^{|I|-|J|}}.
\]
For example, the $u$-variables of $\mathscr P_2$ are
\[
	u_{1}  = \frac{x_1 x_{123}}{x_{12}x_{13}},\quad 
	u_{2}  = \frac{x_2 x_{123}}{x_{12}x_{23}},\quad
	u_{3}  = \frac{x_3 x_{123}}{x_{13}x_{23}},\quad
	u_{12} = \frac{x_{12}}{x_{123}},\quad 
	u_{13} = \frac{x_{13}}{x_{123}},\quad
	u_{23} = \frac{x_{23}}{x_{123}}.
\]
They satisfy the following equtions
\begin{align*}
	&1-u_{1}=u_{2} u_{3} u_{23}^2,
	1-u_{2}=u_{1} u_{3} u_{13}^2,
	1-u_{3}=u_{1} u_{2} u_{12}^2,\\
	&1-u_{12}=u_{3} u_{13} u_{23},
	1-u_{13}=u_{2} u_{12} u_{23},
	1-u_{23}=u_{1} u_{12} u_{13}.
\end{align*}
We will discuss these $u$-equations in the next subsection.

For a $n$-dimensional general permutahedron $\mathscr A$, it can be achieved 
from $\mathscr P_n$ by setting $S_J$ to be $0$ for any 
$J\in \mathscr P_n-\mathscr A$. Facets of $\mathscr A$ are degenerations of facets 
of $\mathscr P_n$ eq.\eqref{Pnfacet}, but some of them become spurious. If a pole
is spurious, it can be written as a positive linear combination of some true facets.
Such relations are sequence of eq.\eqref{SinF} for $I\not\in \mathscr A$.
For example, for $\mathscr A=\{123,12,23,1,2,3\}$, we have that
\[
	0=S_{13}=F_{13}-F_{1}-F_{3},
\]
so $F_{13}$ is not a true facet of $\mathscr A$, there're only $5$ facets left in
$\mathscr A$.

(Zhenjie: what are the facets of general permutahedra?  I believe they are known.)
